% The cover letter sent to the journal upon submission

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Set a class and general configuration
\documentclass[a4paper,onecolumn,10pt]{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Set variables with the title, authors, etc.

\input{information.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Import the required packages
\usepackage[utf8]{inputenc}
\usepackage[TU]{fontenc}
\usepackage[british]{babel}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{geometry}
\usepackage{microtype}
\usepackage{xcolor}
% improved urls with proper hyphenation
\usepackage{xurl}
% Use a different font
\usepackage[scaled=1.1]{notomath}
% Control the font size
\usepackage{anyfontsize}
\usepackage{setspace}
% Generate random text
\usepackage{lipsum}
% Better left and right align
\usepackage{ragged2e}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Configuration of the document

\geometry{%
  left=25mm,
  right=25mm,
  top=15mm,
  bottom=15mm,
  headsep=15mm,
  headheight=15mm,
  footskip=7mm,
  includehead=true,
  includefoot=true
}

% Control line spacing
\onehalfspacing
\newcommand{\Padding}{\vspace{0.75cm}}

% Custom colors
\definecolor{darkgray}{gray}{0.4}
\definecolor{mediumgray}{gray}{0.5}
\definecolor{lightgray}{gray}{0.9}
\definecolor{mediumblue}{HTML}{2060c2}
\definecolor{lightblue}{HTML}{f7faff}

% Make urls use the same font as every other text
\urlstyle{same}

% Configure hyperref and add PDF metadata
\hypersetup{
    colorlinks,
    allcolors=mediumblue,
    pdftitle={Cover letter -- \Title},
    pdfauthor={\AuthorShort},
    breaklinks=true,
}

% Remove numbering and headers and footers
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\begin{flushright}
    Jane Herdman Building
    
    4 Brownlow Street
    
    Liverpool
    
    United Kingdom
    
    L69 3GP
    
    I.Uppal@liverpool.ac.uk
    
    20th May 2025

\end{flushright}

\begin{flushleft}
    \Journal
    
    Editorial Team
    
    Burlington House
    
    London
    
    United Kingdom
    
    W1J 0BQ
\end{flushleft}

\noindent
Dear Editors,

We are pleased to have the opportunity to submit our original research paper entitled ``\Title{}'' for
consideration by \Journal{}. This paper will be part of my (India Uppal’s) doctoral thesis.

The paper presents a novel adaptation of the equivalent sources technique, dual-layer gradient-boosted equivalent sources, for interpolating magnetic data and predicting the anomalous magnetic field from total-field anomaly data. The method addresses key limitations of existing adaptations by employing a dual-layer approach to improve the fit to both short- and long-wavelengths and mitigate the border effects. To enhance the computational efficiency, the approach incorporates block-averaging and the gradient-boosted equivalent sources method, whilst block K-fold cross-validation is used to assist with optimal parameter selection for the model. The method was tested on synthetic datasets and the ICEGRAV aeromagnetic dataset from the British Antarctic Survey, demonstrating the improved fit to the data and ability to predict the amplitude of the anomalous field from total-field anomaly data.

The manuscript is currently available as a preprint on EarthArXiv at \url{https://doi.org/\PreprintDOI} under the CC-BY license. All the code and data needed to reproduce our results are also provided through \url{https://doi.org/\ArchiveDOI} and GitHub repository \url{https://github.com/\GitHubRepository}, both of which are linked in the paper.

Thank you for your consideration of our manuscript. We believe this paper fits very well within the scope of Geophysical Journal International and look forward to your response.

\begin{flushleft}
  Yours Faithfully,
  
  India Uppal (on behalf of all authors)
  \\[0.25cm]
  {
    \color{mediumgray}
    \small
    Department of Earth, Ocean and Ecological Sciences
    
    School of Environmental Science
    
    University of Liverpool

  }
\end{flushleft}
\end{document}
